Lattices of acyclic pipe dreams

### 2023-03-17 acyclicFacets/draft/latticePipeDreams.tex
another minor change

Since $\linearExtensions(I)\neq \varnothing$ if and only if $I$ is acyclic by \cref{lem:linearExtensionsAcyclic}, and~$\linearExtensions(I) \ne \linearExtensions(J)$ for~$I \ne J$ by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:partition}, we have the following straight forward corollary.

>>>>

Since $\linearExtensions(I)\neq \varnothing$ if and only if $I\in \subwordAcyclicFacets(Q,\omega)$ (i.e. $I$ is an acyclic facet) by \cref{lem:linearExtensionsAcyclic}, and also~$\linearExtensions(I) \ne \linearExtensions(J)$ for~$I \ne J$ by \cref{thm:linearExtensionsPartitionSubwordComplexA}~\eqref{item:partition}, we have the following straight forward corollary.
